### 2018-05-23 Sections/economics_of_the_quantum_internet.tex
Ent purification

As discussed in Sec.~\ref{sec:bitcoin_blockchain}, the Bitcoin mining process involves finding bit-strings that hash under SHA256\index{SHA256} to a value within some relatively small range. This so-called `proof-of-work' principle associates computational complexity with the mining process, and since the hashing functions are one-way functions, they must be evaluated via brute-force trial-and-error to find hits.

However, what a waste this is! Our proof-of-work is nothing more than hashing a huge number of random bit-strings, computations which are of no intrinsic value to anyone. The market value in turn has nothing to do with any inherent value earned during the mining process. Rather it is based purely on the psychology of scarcity, since there is an upper bound on the number of Bitcoins that satisfy the legitimacy constraint.

What if we were to replace brute-force hashing of random data with computations of genuine monetary value? Then we would have a sounder currency, whose value derives from the monetary cost of executing useful computations. While it is not so easy to invent such a protocol for classical computation, the idea lends itself very naturally to quantum computation, owing to their ability to undergo encrypted computation and be subject to verification protocols.

Building upon some of the pricing models introduced earlier in this section, there are two main candidates for backing a cryptocurrency with quantum compute-time: the spot market (i.e we execute the computation immediately); and the futures market (i.e we own the right to utilise the computer at some fixed time in the future). We consider the merits of both these candidates.

>>>>

As discussed in Sec.~\ref{sec:bitcoin_blockchain}, the Bitcoin\index{Bitcoin} mining\index{Mining (cryptocurrencies)} process involves finding bit-strings that hash\index{Hash functions} under SHA256\index{SHA256} to a value within some relatively small range. This so-called `proof-of-work'\index{Proof-of-work} principle associates computational complexity with the mining process, and since the hashing functions are one-way functions, they must be evaluated via brute-force trial-and-error to find hits.

However, what a waste this is! Our proof-of-work is nothing more than hashing a huge number of random bit-strings, computations which are of no intrinsic value to anyone. The market value in turn has nothing to do with any inherent value earned during the mining process. Rather it is based purely on the psychology of scarcity\index{Scarcity}, since there is an upper bound on the number of Bitcoins that satisfy the legitimacy constraint.

What if we were to replace brute-force hashing of random data with computations of genuine monetary value? Then we would have a sounder currency, whose value derives from the monetary cost of executing useful computations. While it is not so easy to invent such a protocol for classical computation, the idea lends itself very naturally to quantum computation, owing to their ability to undergo encrypted computation\index{Encrypted quantum computation} and be subject to verification protocols\index{Verification protocols}.

Building upon some of the pricing models introduced earlier in this section, there are two main candidates for backing a cryptocurrency with quantum compute-time: the spot market\index{Spot market} (i.e we execute the computation immediately); and the futures market\index{Futures market} (i.e we own the right to utilise the computer at some fixed time in the future). We consider the merits of both these candidates.

### 2018-05-23 Sections/quality_of_service.tex
Ent purification

Entanglement purification (or distillation) a process by which two imperfect distributed Bell pairs can be condensed into a single Bell pair of higher quality (as measured by a fidelity metric, Sec.~\ref{sec:fid_metric}).

More concretely, we distribute two Bell pairs of fidelity $F$ between Alice and Bob, who perform local operations to reduce them to a single Bell pair of higher fidelity,
\begin{align}
\ket{\Phi^+_F}_{A,B}\otimes\ket{\Phi^+_F}_{A,B} \to \ket{\Phi^+_{F'}}_{A,B},
\end{align}
where,
\begin{align}
F'>F.	
\end{align}

>>>>

Entanglement purification (or distillation) is a process by which two imperfect distributed Bell pairs can be condensed into a single Bell pair of higher quality (as measured by a fidelity metric, Sec.~\ref{sec:fid_metric}).

More concretely, we distribute two Bell pairs of fidelity $F$ between Alice and Bob. Let us assume a dephasing error model in this instance, in which case the imperfect Bell pairs are of the form,
\begin{align}
\hat\rho^F_{A,B} = F\ket{\Phi^+}\bra{\Phi^+} + (1-F)\hat{X}_1\ket{\Phi^+}\bra{\Phi^+}\hat{X}_1,	
\end{align}
which corresponds to a bit-flip error model (Sec.~\ref{sec:dephasing_error}). Alice and Bob then perform their entanglement purification protocol -- operations to reduce them to a single Bell pair of higher fidelity,
\begin{align}
\mathcal{E}_\text{purif}(\hat\rho^{F_\text{in}}_{A,B} \otimes \hat\rho^{F_\text{in}}_{A,B}) \to \hat\rho^{F_\text{out}}_{A,B},
\end{align}
where,
\begin{align}
F_\text{out}>F_\text{in}.
\end{align}

The purification process $\mathcal{E}_\text{purif}$ is realised very simply by Alice and Bob both performing Bell projections (Sec.~\ref{sec:bell_proj}) on their two qubits, classically communicating their measurement outcomes, and performing appropriate local corrections. This is best illustrated by example.

For this model, we will assume our Bell projections destroy the first of their two input qubits, while the second one remains as the output. Then two such projections project a four-qubit state down to a two-qubit state as desired.

Suppose there was no error. Then the input state was,
\begin{align}
\ket\psi_\text{in} &= \ket{\Phi^+}\bra{\Phi^+} \otimes \ket{\Phi^+}\bra{\Phi^+}\\
&= \frac{1}{2}(\ket{0}_1\ket{0}_2+\ket{1}_1\ket{1}_2)(\ket{0}_3\ket{0}_4+\ket{1}_3\ket{1}_4).\nonumber
\end{align}
Now upon inspection it is evident that if a Bell projection between Alice's two qubits (1 and 3) yields the $\ket{\Phi^+}$ outcome, Bob's projection (2 and 4) must also yield $\ket{\Phi^+}$. Similarly, whatever Bell outcome Alice measures, Bob will measure the same outcome. Upon classically communicating that they measured consistent outcomes, they are satisfied the final state is error-free, and it is.

Now suppose there was a bit-flip error on the first qubit of the first pair. Now the input state is,
\begin{align}
\ket\psi_\text{in} &= \hat{X}_1 \ket{\Phi^+}\bra{\Phi^+}\hat{X}_1 \otimes \ket{\Phi^+}\bra{\Phi^+}\\
&= \frac{1}{2}(\ket{1}_1\ket{0}_2+\ket{0}_1\ket{1}_2)(\ket{0}_3\ket{0}_4+\ket{1}_3\ket{1}_4).\nonumber
\end{align}
Upon performing the Bell measurements as before, suppose Alice measures the $\ket{\Psi^+}$ outcome. Now Bob must measure the $\ket{\Phi^+}$ outcome, and a comparison of measurement outcomes diagnoses this single bit-flip error, which may subsequently be corrected with an additional bit-flip.

In the above two scenarios (no error, or exactly one error), the state is correctable to a perfect Bell pair. What if there are two errors? Consider the input state with bit-flips affecting both Bell pairs. Then,
\begin{align}
\ket\psi_\text{in} &= \hat{X}_1 \ket{\Phi^+}\bra{\Phi^+}\hat{X}_1 \otimes \hat{X}_3\ket{\Phi^+}\bra{\Phi^+}\hat{X}_3\\
&= \frac{1}{2}(\ket{1}_1\ket{0}_2+\ket{0}_1\ket{1}_2)(\ket{1}_3\ket{0}_4+\ket{0}_3\ket{1}_4).\nonumber
\end{align}
Upon performing the Bell projections, both Alice and Bob are guaranteed to measure the same outcome, as per the error-free case. However this isn't error-free at all since the remaining state is $\ket{\Psi^+}$ not $\ket{\Phi^+}$. That is, the bit-flip error has permeated through to the corrected state.

Following this example it is evident that our rudimentary entanglement purification protocol can correct at most one bit-flip error. For this reason a mixed state is only correctable if \mbox{$F>1/2$} to begin with. Otherwise errors are more likely to permeate than be corrected, thereby reducing output fidelity.

Similar reasoning as above can be employed to correct against phase-flip errors, and depolarising errors more generally.
